Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-08-18 prob.tex
prob.tex \section{Quantum Probability Spaces} Reorder the definition and example...

The mathematical framework above assumes that there exists a predetermined
set of events that are independent of the particular experiment. However,
in many practical situations, the structure of the event space is
only partially known and the precise dependence of two events on each
other cannot, a priori, be determined with certainty. In the quantum
framework, this partial knowledge is compounded by the fact that there
exist non-commuting events which cannot happen simultaneously. To
accommodate these more complex situations, we abandon the sample space~$\Omega$
and reason directly about events. A quantum probability space therefore
consists of just two components: a set of events $\qevents$ and a
probability measure $\mu:\qevents\rightarrow[0,1]$. We present an
example before giving the formal definition.

\begin{example}[One-qubit quantum probability space] Consider
a one-qubit Hilbert space with states $\ket{\phi}=\alpha\ket{0}+\beta\ket{1}$
such that $|\alpha|^{2}+|\beta|^{2}=1$, $\alpha,\beta\in\C$. The
set of events associated with this Hilbert space consists of all projection
operators. Each event is interpreted as a possible post-measurement
state of a quantum system in current state $\ket{\phi}$. For example,
the event $\proj{0}$ indicates that the post-measurement state will
be~$\ket{0}$; the event $\proj{1}$ indicates that the post-measurement
state will be~$\ket{1}$; the event $\proj{\ps}$ where $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
indicates that the post-measurement state will be $\ket{\ps}$; the
event $\mathbb{1}=\proj{0}+\proj{1}$ indicates that the post-measurement
state will be a linear combination of $\ket{0}$ and $\ket{1}$; and
the empty event $\mathbb{0}$ states that the post-measurement state
will be the empty state. As in the classical case, a probability measure
is a function that maps events to $[0,1]$: here is a partial specification
of a possible probability measure: 
\[
\begin{array}{rcl}
\mu\left(\mathbb{0}\right)=0,\quad\mu\left(\mathbb{1}\right)=1,\quad\mu\left(\proj{0}\right)=1,\quad\mu\left(\proj{1}\right)=0,\quad\mu\left(\proj{\ps}\right)=1/2,\quad\ldots\end{array}
\]
Note that, similarly to the classical case, the probability of $\mathbb{1}$
is 1 and the probability of collections of orthogonal events (e.g.,
$\proj{0}+\proj{1}$) is the sum of the individual probabilities.
A collection of non-orthogonal events (e.g., $\proj{0}$ and $\proj{\ps}$)
is however not even a valid event. In the classical example, we argued
that each probability measure is uniquely determined by two actual
coins. A similar (but much more subtle) argument is valid also in
the quantum case. By postulates of quantum mechanics and Gleason's
theorem, it turns out that for large enough quantum systems, each
probability measure is uniquely determined by an actual quantum state.
\qed\end{example}

To properly explain the previous example and generalize to arbitrary
quantum systems, we formally discuss projection operators, 
define quantum probability measures, and extend to quantum interval-valued
probability.

@@

\begin{definition}[Projection Operators;
Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}.} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Griffiths2003,Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_1$ and $P_2$ are \emph{orthogonal} if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
is also a projection operator if and only if they are orthogonal, 
where the preposing subscript $\mathscr{O}$
means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators. 
\item Conversely, every projection~$P$ can be expressed as $\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ which
has an orthonormal basis~$\{\ket{\psi_{j}}\}_{j=1}^{N}$. 
\end{itemize}
\qed\end{definition}

>>>>

The mathematical framework above assumes that there exists a predetermined
set of events that are independent of the particular experiment. However,
in many practical situations, the structure of the event space is
only partially known and the precise dependence of two events on each
other cannot, a priori, be determined with certainty. In the quantum
framework, this partial knowledge is compounded by the fact that there
exist non-commuting events which cannot happen simultaneously. To
accommodate these more complex situations, we abandon the sample space~$\Omega$
and reason directly about events. A quantum probability space therefore
consists of just two components: a set of events $\qevents$ and a
probability measure $\mu:\qevents\rightarrow[0,1]$. To properly explain
the quantum probability, we will first discuss projection operators
as quantum events, provide an easy example, define quantum probability
measures, and extend to quantum interval-valued probability.

@@

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393},
or an elementary quantum test~\cite{peres1995quantum}.} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$
onto a linear subspace~$S$ of $\Hilb$. The set of all events~$\events$
can be defined recursively as follow: \footnote{``Projection'' is sometimes called ``orthogonal projection\textquotedbl{}
or ``self-adjoint projection\textquotedbl{} to emphasize $P^{\dagger}=P$~\cite{Griffiths2003,Maassen2010}.} 
\begin{itemize}
\item $\mathbb{0}$ is a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_{1}$ and $P_{2}$ are \emph{orthogonal} if
$P_{1}P_{2}=P_{2}P_{1}=\mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
is also a projection operator if and only if they are orthogonal,
where the preposing subscript $\mathscr{O}$ means $\tensor*[_{\mathscr{O}}]{+}{}$
is an operation between operators. 
\item Conversely, every projection~$P$ can be expressed as $\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ which
has an orthonormal basis~$\{\ket{\psi_{j}}\}_{j=1}^{N}$. 
\end{itemize}
\qed\end{definition}

We present an example before giving the formal definition of quantum
probability measures.

\begin{example}[One-qubit quantum probability space] Consider
a one-qubit Hilbert space with states $\ket{\phi}$, which can be
expressed as a linear combination of $\ket{0}$ and $\ket{1}$, i.e.,
$\ket{\phi}=\alpha\ket{0}+\beta\ket{1}$ such that $|\alpha|^{2}+|\beta|^{2}=1$,
$\alpha,\beta\in\C$. The set of events associated with this Hilbert
space consists of all projection operators. Each event is interpreted
as a possible post-measurement state of a quantum system in current
state $\ket{\phi}$. For example, the event $\proj{0}$ indicates
that the post-measurement state will be $\ket{0}$; the event $\proj{1}$
indicates that the post-measurement state will be $\ket{1}$; the
event $\proj{\ps}$ where $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
indicates that the post-measurement state will be $\ket{\ps}$; the
event $\mathbb{1}=\proj{0}\tensor*[_{\mathscr{O}}]{+}{}\proj{1}$
indicates that the post-measurement state will be a linear combination
of $\ket{0}$ and $\ket{1}$; and the empty event $\mathbb{0}$ states
that the post-measurement state will be the empty state. As in the
classical case, a probability measure is a function that maps events
to $[0,1]$: here is a partial specification of a possible probability
measure: 
\[
\begin{array}{rcl}
\mu\left(\mathbb{0}\right)=0,\quad\mu\left(\mathbb{1}\right)=1,\quad\mu\left(\proj{0}\right)=1,\quad\mu\left(\proj{1}\right)=0,\quad\mu\left(\proj{\ps}\right)=1/2,\quad\ldots\end{array}
\]
Note that, similarly to the classical case, the probability of $\mathbb{1}$
is 1 and the probability of collections of orthogonal events (e.g.,
$\proj{0}+\proj{1}$) is the sum of the individual probabilities.
A collection of non-orthogonal events (e.g., $\proj{0}$ and $\proj{\ps}$)
is however not even a valid event. In the classical example, we argued
that each probability measure is uniquely determined by two actual
coins. A similar (but much more subtle) argument is valid also in
the quantum case. By postulates of quantum mechanics and Gleason's
theorem, it turns out that for large enough quantum systems, each
probability measure is uniquely determined by an actual quantum state.
\qed\end{example}
